%\documentclass[sigconf, authordraft]{acmart}
\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{listings} % For formal tables
\usepackage[font=small,skip=0pt]{caption}
% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[Fire-IRLeD'17]{Forum for Information Retrieval Evaluation}{Dec 2017}{IISc, Bangalore, India} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{XX.00}

\acmSubmissionID{123-A12-B3}

\begin{document}
\title{Using Regular Expressions, Word Embedding and Topic Modeling to Find Cited Legal Documents}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Yogesh H. Kulkarni}
\orcid{0000-0001-5431-5727}
\affiliation{%
  \institution{Consultant, RightSteps Consultancy,}
  \city{Pune, India.} 
}
\email{yogeshkulkarni@yahoo.com}

\author{Rishabh Patil}
\affiliation{%
  \institution{Engineer, RightSteps Consultancy,}
  \city{Pune, India.} 
}
\email{rishabh@rightstepsconsultancy.com}

\author{Srinivasan Shridharan}
\affiliation{%
  \institution{Founder, RightSteps Consultancy,}
  \city{Pune, India.} 
}
\email{srini@rightstepsconsultancy.com}
% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Yogesh Kulkarni et al.}


\begin{abstract}
Indian judicial system follows ``Common Law System'' which refers to written-law(statute) as well as past cases (precedent) to give verdict on the legal cases. Due to thousands of past cases it becomes tedious and error-prone to find relevant precedent, manually. An automatic precedent retrieval system is the need of the hour. One of the key requirements of such information system is to find cases which could be ``similar'' to the case in hand. The ``similarity'' used in this paper is about citations. The problem is of predicting prior cases which  could potentially be cited by a particular case text. This paper proposes such association system using mixed approaches. It employs rule-based Regular Expressions based on references to statute and Articles. It finds cosine similarity between cases using vectors generated by popular word embedding called doc2vec. It also leverages topic modeling by finding matches between cases based on the  number of common topic words. Towards end, this paper demonstrates efficacy of the proposed system by generating cite-able documents from test data-set.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003317.10003318.10003320</concept_id>
<concept_desc>Information systems~Document topic models</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010179.10003352</concept_id>
<concept_desc>Computing methodologies~Information extraction</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Document topic models}
\ccsdesc[500]{Computing methodologies~Information extraction}



\keywords{Information Retrieval, Regular Expressions, Word Embedding, Topic Modeling, Legal, Word2Vec,  Citations, NLP.}


\maketitle

\interfootnotelinepenalty=8000

\input{rightstepspune_track2_workingnotes_body-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{rightstepspune_track2_workingnotes-bibliography} 

\end{document}
