%\documentclass[sigconf, authordraft]{acmart}
\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{listings} % For formal tables
\usepackage[font=small,skip=0pt]{caption}
% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[Fire-IRLeD'17]{Forum for Information Retrieval Evaluation}{Dec 2017}{IISc, Bangalore, India} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{XX.00}

\acmSubmissionID{123-A12-B3}

\begin{document}
\title{Using Conditional Random Fields to Detect Catchphrases in Legal Documents}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Yogesh H. Kulkarni}
\orcid{0000-0001-5431-5727}
\affiliation{%
  \institution{Consultant, RightSteps Consultancy,}
  \city{Pune, India.} 
}
\email{yogeshkulkarni@yahoo.com}

\author{Rishabh Patil}
\affiliation{%
  \institution{Engineer, RightSteps Consultancy,}
  \city{Pune, India.} 
}
\email{rishabh@rightstepsconsultancy.com}

\author{Srinivasan Shridharan}
\affiliation{%
  \institution{Founder, RightSteps Consultancy,}
  \city{Pune, India.} 
}
\email{srini@rightstepsconsultancy.com}
% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Yogesh Kulkarni et al.}


\begin{abstract}
``Common Law System'' practiced in India refers to statute as well as precedent to form judgments. As number of cases are increasing rapidly, an automatic precedent retrieval system is desirable. One of the key requirements of such information retrieval system is to pre-populate database of prior cases with catchphrases for better indexing and faster, relevant retrieval. This paper proposes an automatic catchphrases prediction for cases for the same. The problem catchphrase detection has been modeled as ``custom named entity recognition (NER) using conditional random fields (CRF)''. CRF is trained with pairs of prior cases and their respective catchphrases, the gold standards. The model is, then used to predict catch-phases of unseen legal texts.  Towards end, this paper demonstrates efficacy of the proposed system using practical data-set.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003317.10003338.10003340</concept_id>
<concept_desc>Information systems~Probabilistic retrieval models</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010178.10010179.10003352</concept_id>
<concept_desc>Computing methodologies~Information extraction</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}


\ccsdesc[500]{Computing methodologies~Information extraction}
\ccsdesc[500]{Information systems~Probabilistic retrieval models}


\keywords{Information Retrieval, Conditional Random Fields, Named Entity Recognition, Legal, Text Mining, Natural Language Processing.}


\maketitle

\interfootnotelinepenalty=8000

\input{rightstepspune_track1_workingnotes_body-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{rightstepspune_track1_workingnotes-bibliography} 

\end{document}
